% to compile:
% bibtex project
% bibtex project
% pdflatex project

\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{graphicx}
\graphicspath{ {./images/} }

\title{A Domain-Specific Knowledge Graph for News Item Recommendations and Information Retrieval}
\author{Author: Christopher Eaves-Kohlbrenner \\ Supervisor: Michael Zakharyaschev}

\begin{document}
\maketitle

\begin{center}
\hfill \break
\hfill \break
\hfill \break
MSc Data Science project\\
Department of Computer Science and Information Systems\\
Birkbeck College, University of London\\
2021\\
\hfill \break
\hfill \break
\hfill \break

\textit{This report is substantially the result of my own work, expressed in my own words, except where explicitly indicated in the text. I have read and understood the sections on plagiarism in the Programme Handbook and the College web site. I give my permission for it to be submitted to the JISC Plagiarism Detection Service. \\
\hfill \break
The report may be freely copied and distributed provided the source is explicitly acknowledged.}
\end{center}

% \end{center}

\newpage
\begin{abstract}
TBD...
\end{abstract}

\newpage
\tableofcontents

\newpage
\section{Introduction}
Introduction
\subsection{Problem}
Problem...
\subsection{Project Objectives}
Project Objectives...
\subsection{Summary of Findings}
Summary of Findings...
\subsection{Report Outline}
Report Outline...
\subsection{Technical Specifications}
Technical Specifications...

\section{Context and Background}
\subsection{Knowledge Graphs}
\subsection{Network stuff?}
similar to this?
https://www.dcs.bbk.ac.uk/r/studentprojects/exampleprojects/msc/

"A graph neural network path to network centralities.pdf"


\section{Data}

What is Reuters data set, how did I get it, etc.

Jupyter notebook -- data exploration and preprocessing, diagrams, histograms, etc.

Simple dimensions (properties like subjects, genres, word count) and complex NLP ones (XML body)

Challenges / edge cases: https://github.com/heychrisek/msc-data-science-project/ - 5x-challenges

\subsection{Data Set Collection}
\subsection{Data Input and Preprocessing}


\section{Knowledge Graph Design and Implementation}

Continuation of previous section (Data Input and Preprocessing), load into Neo4j...

\subsection{Graph Database Creation}
Neo4j ingest
\subsection{Semantic Enhancements}
\subsection{Natural Language Processing}
\subsection{Models, etc.???}

\section{Knowledge Graph performance evaluation}
\subsection{Interpretability}
\subsection{Others...confusion matrix, predictions, clustering, betweenness, etc.}

\section{Conclusions}
\subsection{Future Work}
\subsection{Conclusion}

\section{Appendix}


\newpage
\bibliographystyle{abbrv}
\bibliography{proposal}

\end{document}